Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2017-12-23 paper-ieee-trans.tex
Update paper-ieee-trans.tex

\begin{abstract}
From the advent of Grid technology as the new paradigm of distributed
computing to the current days of Cloud computing models, the continuous need
of new tools and services to match the scientific community requirements has been
addressed in Europe by the creation of software development and
e-Infrastructure coordination dedicated projects. This work examines the
evolution of the software engineering methodologies used in past and present
European Commission-funded software projects to illustrate how the research on software
reliability has progressed in Europe over the last 15 years following the
foundation of the first project in 2001. In particular, we describe the team
organizational structure, techniques and procedures that have guided the Quality
Assurance definitions in order to deliver quality software. We highlight the challenges
and barriers that have been faced throughout these years and how to overcome them totally or
partially. To conclude, we discuss the future directions of software
Quality Assurance methodologies for the incoming projects.
\end{abstract}

>>>>

\begin{abstract}
From the advent of Grid technology as the new paradigm of distributed
computing to the current days of Cloud computing models, the continuous need
of new tools and services to match the scientific community requirements has been
addressed in Europe by a various number of European Commission funded software development
and e-Infrastructures creation, operation and management dedicated projects.
% the creation of software development and e-Infrastructure coordination dedicated projects. 
This work examines the evolution of the software engineering methodologies used in past and present
European Commission-funded projects to illustrate how the research on software
reliability has progressed in Europe over the last 15 years following the
foundation of the first project in 2001. In particular, we describe the team
organizational structure (?), techniques and procedures that have guided the Quality
Assurance definitions in order to deliver quality software. We highlight the challenges
and barriers that have been faced throughout these years and how they were overcomed totally or
partially. To conclude, we discuss possible future directions in software
Quality Assurance methodologies for the upcoming projects.
\end{abstract}
